---
title: "p8105_hw4_yx2450"
output: html_document
---

In Problems 1 and 2, I worked with Manqi Cai (UNI: mc4433).

```{r}
library(tidyverse)
library(janitor)
library(readxl)
library(ggridges)
library(ggthemes)
library(pander)
```

### Problem 1
```{r}
pups_data = read_csv("./data/FAS_pups.csv", col_types = "ciiiii") %>% 
  clean_names() %>% 
  mutate(sex = recode(sex, `1` = "male", `2` = "female"))

pups_tidy_data = gather(pups_data, key = PD_outcome, value = days, pd_ears: pd_walk) %>% 
  drop_na()
```

The collaborator will create a plot showing the distribution of post-natal days for each developmental landmark.
```{r}
#a plot showing the distribution of post-natal days for each developmental landmark.
#plot a scatter plot for distribution of post-natal days for each developmental landmark.
pups_tidy_data %>% 
  group_by(PD_outcome) %>% 
  ggplot(aes(x = litter_number, y = days, color = PD_outcome)) +
  geom_point(alpha = .4) +
  facet_grid(. ~PD_outcome)+
  theme_bw()


#plot a density plot for distribution of post-natal days for each developmental landmark.
pups_tidy_data %>%
  ggplot(aes(x = days, y = PD_outcome, color = PD_outcome)) +
  geom_density_ridges(aes(color = PD_outcome), scale = .75)+
  theme_bw()

```
From the plots depicted above, we can see that the post-natal days for pd_ears, pd_eyes, pd_pivot and pd_walk are centralized around 3-5, 12-14, 5-8, and 8-11. 


The GitHub repo containing our solution to this problem is [here](https://github.com/monkeydnear/p8105_hw4_yx2450).


### Problem 2

The GitHub repo containing the solution to this problem is [here](https://github.com/caimanqi/p8105_hw4_problem2_yx2450_mc4433)


### Problem 3

My personal website is [here](http://jeffgoldsmith.com)
